\documentclass[a4paper,12pt]{article} % Set documentclass article and set font size

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Packages

\usepackage[utf8]{inputenc}
\usepackage[british]{babel}
\usepackage[british]{isodate}
\usepackage{csquotes}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{tabularx}
\usepackage[
backend=biber,
style=apa,
sorting=nyt, % Sort by name, year, title
backref=true,
dateabbrev=false,
language=british,
urldate=long
]{biblatex}
\usepackage{xcolor}
\usepackage[toc,page]{appendix}
\usepackage{svg}
\usepackage{float}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{multirow,multicol,makecell,booktabs}
\usepackage[justification=centering]{caption}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{ragged2e}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{rotating}
\usepackage{hyperref} % Load after everything else
\usepackage[symbols, nopostdot, automake, nonumberlist]{glossaries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Custom Settings

\addbibresource{master_thesis.bib} % Add bibliography source

\setlength\bibitemsep{1.5\itemsep} % Adjust distance of reference entries

\renewcommand*\appendixpagename{\Large Appendices} % Adjust size of title of the appendices section

\renewcommand*{\finentrypunct}{}
\renewbibmacro*{pageref}{%
  \addperiod% NEW
  \iflistundef{pageref}
    {}
    {\newline\footnotesize\printtext[parens]{%
       \ifnumgreater{\value{pageref}}{1}
         {\bibstring{backrefpages}\ppspace}
     {\bibstring{backrefpage}\ppspace}%
       \printlist[pageref][-\value{listtotal}]{pageref}}}}%
\DefineBibliographyStrings{english}{
  backrefpage={Cited on page},
  backrefpages={Cited on pages}
}

\geometry{ % Adjust paper geometry
 a4paper,
 right=25mm,
 bottom=20mm,
 left=25mm,
 top=25mm}
\urlstyle{same} % Make URL font the same with the rest of the document
\onehalfspacing % Adjust spacing
%\setstretch{1.75}
%\doublespacing
\allowdisplaybreaks % Allow for breaks in equations across pages
\addto\captionsbritish{ % Replace "english" with the language you use
  \renewcommand{\contentsname}%
    {Table of Contents}%
} % Adjust title of the table of contents
\numberwithin{equation}{section} % Number equations with sections
\numberwithin{figure}{section}
\numberwithin{table}{section}
%\setcounter{tocdepth}{2} % Set maximum level to which sections are displayed in the table of contents

\newcommand{\appendixsubsection}[1]{
    \stepcounter{subsection}
    \subsection*{\Alph{section}.\arabic{subsection}\hspace{1em}{#1}}
}


\pagestyle{plain}

% Define a custom name format that prints names of authors in references in bold
\DeclareNameWrapperFormat{sortname}{\mkbibbold{#1}}
\DeclareNameWrapperAlias{author}{sortname}

% Add definition format
\newtheorem{definition}{Definition}

% Make links of glossary entries black
\makeatletter
\newcommand*{\glsplainhyperlink}[2]{%
    \begingroup%
      \hypersetup{hidelinks}%
      \hyperlink{#1}{#2}%
    \endgroup%
}
\let\@glslink\glsplainhyperlink
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Glossary
\makeglossaries 

% Glossary entries
\newglossaryentry{nk}{
name=NK,
description={New Keynesian}
}

\newglossaryentry{ha}{
name=HA,
description={Heterogeneous Agent(s)}
}

\newglossaryentry{hank}{
name=HANK,
description={Heterogeneous Agent New Keynesian}
}

\newglossaryentry{gfc}{
name=GFC,
description={Great Financial Crisis}
}

\newglossaryentry{ltv}{
name=LTV,
description={Loan-to-Value}
}

\newglossaryentry{dsge}{
name=DSGE,
description={Dynamic Stochastic General Equilibrium}
}

\newglossaryentry{egm}{
name=EGM,
description={Endogenous Gridpoints Method}
}

\newglossaryentry{iou}{
name=IOU,
description={I Owe You}
}

\newglossaryentry{ghh}{
name=GHH,
description={Greenwood-Hercowitz-Huffman (\cite{ghh1988})}
}

\newglossaryentry{ar}{
name=AR,
description={Autoregressive}
}

\newglossaryentry{zlb}{
name=ZLB,
description={Zero Lower Bound}
}

\newglossaryentry{mpc}{
name=MPC,
description={Marginal Propensity to Consume}
}

\newglossaryentry{fof}{
name=FoF,
description={Flow of Funds}
}

\newglossaryentry{nkpc}{
name=NKPC,
description={New Keynesian Phillips Curve}
}

\newglossaryentry{foc}{
name=FOC,
description={First Order Condition}
}

\newglossaryentry{irf}{
name=IRF,
description={Impulse Response Function}
}

\newglossaryentry{crra}{
name=CRRA,
description={Constant Relative Risk Aversion}
}

\newglossaryentry{gdp}{
name=GDP,
description={Gross Domestic Product}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% hyperref package
\usepackage{footnotebackref} % Brings you back to where the footnote is in the text
\hypersetup{ 
    colorlinks,
    linkcolor=blue,
    filecolor=blue,  
    citecolor=blue,
    urlcolor=blue} % Setup with the hyperref package

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formalities
\title{Technology Choice and Firm Composition in an RBC Model with Endogenous Entry}
\author{}
\date{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Begin Document
\begin{document}
\selectlanguage{british}
\pagenumbering{gobble} % Turn page numbering off
\maketitle % Create title

\vspace{4cm}
\begin{center}
Master Thesis Presented to the\\
Department of Economics at the\\
Rheinische Friedrich-Wilhelms-Universität Bonn\\
\vspace{1cm}
In Partial Fulfillment of the Requirements for the Degree of\\
Master of Science (M.Sc.)
\end{center}

\vspace{5cm}
\begin{center}
\begin{tabular}{ l l }
Supervisors: & Prof.~Dr.~Christian Bayer \\
& Dr.~Zheng Gong \\
& \\
& \\
Date of Submission: & \printdate{2025-7-1}\\
Author: & Enrico Truzzi\\
Matriculation Number: & 50182495
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\pagenumbering{roman} % Turn page numbering to small roman
\setcounter{tocdepth}{2}
{ \hypersetup{hidelinks} \tableofcontents } % Hide links in table of contents

\newpage
{ \hypersetup{hidelinks} \listoffigures } % Hide links in list of figures

\newpage
{ \hypersetup{hidelinks} \listoftables } % Hide links in list of tables

% Add here list of acronyms
\newpage
\setlist[description]{leftmargin=!, labelwidth=5em} % Change for glossaries
\printglossary[title=List of Acronyms]
\setlist[description]{style=standard} % Reset settings back to default


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{abstract} % Create abstract

Hello this is abstract bro.

\begin{center}
\rule{10cm}{0.4pt}
\end{center}

\noindent
\textit{JEL Classification:} E12, E21, E32 % JEL topic classification of paper

\noindent
\textit{Keywords:} Firm Heterogeneity, RBC Model % Keywords of paper
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\pagenumbering{arabic} % Turn page numbering to small arabic
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{\leftmark}
\fancyfoot[C]{\thepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\thispagestyle{plain}
\section{Introduction}
\label{sec:introduction}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Literature}
\label{sec:literature}



I first start this review of the literature by addressing \textcite{bilbiie2012endogenous} (henceforth BGM), since it represents the core framework behind the model developed in this thesis. 
BGM expand on a classic RBC model\footnote{See \textcite{campbell1994inspecting}} by introducing monopolistic competition and endogenous firm entry for both a CES preferences and a translog preferences framework. 
Firms incur a one-time sunk entry cost to enter and then start producing after one period with constant returns (time-to-build). 
This one-time sunk entry cost is interpreted in the model as an "investment" paid in effective labor units to create a new firm/variety. Consequently, the economy has two sectors. 
A production sector where incumbent firms produce output using labor and (as an additional exercise) physical capital, and an "entry" or variety-expanding sector, where labor can be used to create new firms/varieties. 

An important aspect of the BGM framework is that each variety is interpreted as a new product line, instead of a new firm in itself. 
Therefore, whenever any reference to the number of varieties is made, it does not necessarily translate to the actual number of firms in the economy. 
The stock of varieties is a state variable that evolves with entry and exit, although in the baseline, the main driver of change is entry, 
since exit happens through a fixed probability "death shock" that affects all firms equally. Because of the sunk costs, entry is forward-looking,
that is, prospective entrants base their entry decisions on the expected present value of profits, which in this framework represents the "stock-market price" of a new firm. 

Aggregate conditions drive entry in the BGM model. In an economic expansion, higher demand and profits raise the value of starting a firm, which naturally induces more entry. 
However, due to the entry cost and, in particular, the time-to-build aspect, new firms enter sluggishly. This slow adjustment in the number of producers creates a novel 
propagation mechanism for shocks. A positive permanent productivity shock, for example, boosts output and profits immediately. However, it also sets off a gradual increase in firm entry, 
which persists even after the initial shock, given that the larger cohort of new firms continues to produce additional output, prolonging the boom. In essence, the increase in 
product variety acts like capital stock in the classic RBC model, building up slowly and sustaining production, enhancing persistence.

Another important feature is that an increase in firm entry (product variety) can affect profits at the firm level and even markups in their translog specification. 
BGM show that their framework produces procyclical profits and a procyclical number of firms, consistent with empirical evidence of net firm creation rising in booms. 
The pricing of a new firm, on the other hand, influences household savings decisions and labor allocation across sectors. If this price rises, households channel more 
labor into firm creation, increasing future variety at the cost of current output. This trade-off is similar to the one found between capital and labor in the classic 
RBC framework that BGM expand upon.

BGM find that introducing endogenous entry significantly improves the RBC model's ability to propagate shocks. The authors argue that this is due to the internal 
persistence mechanism generated by the slow build-up of new firms following a shock that the exogenous entry model lacks. Quantitatively, the model reproduces key 
second moments of macro data at least as well as the standard RBC model without the introduction of capital, and even better than it once capital is introduced. 
In particular, after the introduction of capital, the model can match the observed variance and autocorrelation of GDP seen in the data. The authors, therefore, 
conclude that abstracting away from firm entry/exit dynamics can miss important sources of persistence in business cycles. Their work laid a foundation for many 
subsequent DSGE models with entry, including applications to monetary policy\footnote{See \textcite{bilbiie2007monetary,bergin2008extensive,etro2015new}} and 
open economy/trade contexts\footnote{See \textcite{epifani2011trade,bergin2015international}}

\textcite{sedlavcek2017growth} introduce the other core framework from which I derive the firm heterogeneity and matching friction mechanisms used in this thesis. 
Sedláček and Sterk focus on how the composition of new firm cohorts varies over the business cycle and how this affects aggregate employment dynamics. 
Empirically, the authors document rich evidence using U.S. Business Dynamics Statistics for 1979-2013, finding that employment created by startup cohorts is highly
volatile and procyclical, and these cohort differences persist for many years. Additionally, they find that total employment differences across cohorts are mostly
driven by average firm size rather than by the number of startups. In other words, the authors argue that cohorts born in booms tend to contain firms that grow
larger, whereas recession-born cohorts remain smaller on average. In particular, they show that firms born during the Great Recession were not only fewer in 
number but also exhibited weaker growth potential, which in turn creates a long-lasting drag on aggregate employment at that cohort age. Sedláček and Sterk 
attribute this to selection effects (which types of businesses choose to enter in booms versus in recessions) and heterogeneous growth profiles across startups.

To explain these facts, Sedláček and Sterk develop a DSGE firm dynamics model with heterogeneous startups and entry uncertainty. Firm heterogeneity in the model arises
from differences in each startup's growth potential, modeled via the demand side. That is, new firms can choose to produce either in a low-scalability/"niche" 
environment or in a high-scalability/"mass market" environment, which is captured by the heterogeneous returns-to-scale parameters found in each environment. 
This choice at birth essentially represents a type-draw and it determines the firm's growth trajectory. After birth, firms can choose to expand their customer 
base over time by spending on marketing, subject to diminishing returns. Crucially, highly scalable startups have the incentive to invest aggressively in demand
expansion, since there are larger returns-to-scale to begin with, whereas niche firms cannot profitably scale up as much. 
The model also features an equilibrium entry condition to equalize profits (and thus entry) among different types and a friction resembling congestion in entry,
where the stock of ideas is limited and firms have to compete for entry, especially for highly scalable types.

The key mechanism driving the firm composition dynamics in the Sedláček-Sterk framework is the aggregate conditions at the time of entry. 
A favorable aggregate state disproportionally benefits mass-market firms, which rely primarily on expansion. 
Their model allows for a multitude of aggregate shock types, including preference shocks, productivity shocks, and a composition shock that shifts the distribution of business opportunities. 
They model periods of recession through a composition shock that decreases the stock of high-scalability ideas and increases the stock of 
low-scalability ideas, effectively mimicking the fact that good business opportunities are harder to come by during recessions. As a result, 
booms tend to induce a greater fraction of high-growth potential startups, whereas recessions see a higher share of niche, low-growth firms. 

This endogenous composition effect means that entry in booms is not only higher in quantity but also in quality, which translates to the 
fact that cohorts born during booms end up becoming much larger contributors to employment over time. Thus, initial conditions at birth 
have persistent effects on the path of aggregate employment/labor. In fact, their estimated model shows that most of the variation in 
cohort employment is driven by startup composition at entry, rather than post-entry shocks or decisions. Importantly, this mechanism 
operates gradually, such that the short-run impact of a boom's extra entrants is small, but those high-potential firms scale up and 
produce a long and slow-moving expansion in employment as they age. Conversely, a recession that hinders the potential of the entrant 
firms filtering out high-potential startups will lead to a persistent shortfall in employment and output, as that generation of firms will lack high-scalability startups.

Sedláček and Sterk’s model, when estimated on U.S. data, can explain several observations that are not fully addressed by other DSGE models. 
The model reproduces the fact that employment fluctuations of startups are strongly procyclical and persistent, which the authors 
attribute to the composition effect described above. Their counterfactual analysis indicates that aggregate conditions at birth 
account for the majority of the employment variation across cohorts, consistent with the idea that it is the initial selection of 
firms at birth that matters the most in long-run cohort outcomes. In the aggregate, shocks to startup composition can create large, 
low-frequency movements in employment, thus establishing a novel propagation mechanism for business cycles: cohort effects. 
Even after the shocks dissipate, the cohorts formed under its influence continue to shape growth, a phenomenon that, according to the 
authors, can help explain the slow recovery from the 2008-09 recession. Ultimately, the Sedláček-Sterk framework builds a bridge 
between business cycle research and the entrepreneurship literature, emphasizing that heterogeneity in startup quality is 
macro-relevant through theory and empirical work.

Moving on to the broader literature relevant to the topics discussed in this thesis, I start by discussing foundational work on 
incorporating endogenous firm dynamics in DSGE and RBC frameworks, and then progressively move on to more recent work. 
A first seminal contribution is given by \textcite{ghironi2007trade}, which embeds a heterogeneous-firm trade model into
a two-country dynamic GE setting. The authors show how the number of producers and product variety become state variables
affecting consumption and investment, establishing a baseline for incorporating firm entry in DSGE models. 
Subsequent research by \textcite{jaimovich2008firm} shows that net business formation is strongly procyclical 
and can itself propagate shocks. The authors present a DSGE model where an expansion induces a surge in firm entry, 
which increases competition and drives markups countercyclically lower. This mechanism causes aggregate productivity to 
rise in booms, amplifying output fluctuations. Their findings underscore an important propagation channel 
that is similarly found in the model presented in this thesis.

However, \textcite{bilbiie2012endogenous} probably represents the most influential foundational work in this vein of the literature, 
also starting a line of work that modifies their model to study optimal monetary policy with endogenous firm entry, weighing the benefits 
of variety creation against costs like entry investment and potentially inefficient boom-burst cycles of firm creation (e.g. \textcite{bilbiie2014optimal, lewis2012firm})
Another influential line of work opted for idiosyncratic firm productivity shocks alongside entry as their driver of firm heterogeneity within a DSGE structure. 
An important example is \textcite{clementi2016entry}, who build a quantitative RBC model with endogenous entry and exit, where entrants draw idiosyncratic 
productivity signals, invest, and may exit if unprofitable. A key result presented by the authors that aligns with existing literature is that introducing 
firm heterogeneity greatly increases internal propagation of aggregate shocks in the long run. Notably, earlier work by \textcite{samaniego2008entry} had 
only found modest business-cycle effects of entry in a simpler setting with homogeneous firms. In short, these foundational studies established that 
endogenous firm entry and exit dynamics, coupled with firm heterogeneity, is a potent mechanism for shock propagation. It increases volatility, 
generates endogenous persistence, and introduces new welfare considerations via product variety.

A key extension in recent years is to model heterogeneity in firms' technologies or scale, often endogenously chosen, and study how this 
affects aggregate fluctuations. Excluding \textcite{sedlavcek2017growth}, another interesting contribution to this modeling approach is given 
by \textcite{smirnyagin2023returns}. The author allows entrepreneurs to choose the returns-to-scale of their project upon entry. The resulting 
finding echoes the results in the Sedláček-Sterk framework, where high-returns-to-scale firms are less likely to be started in economic downturns.
The explanation for this phenomenon, however, now comes from firm financing, with the author arguing that large-scale projects require more 
upfront investment or financing, so when profits or credit conditions are weak, entrepreneurs defer their ambitious ideas and only smaller-scale 
firms launch. The author also states that the absence of high-growth firms can hinder recovery in recessions, further corroborating the role of 
firm heterogeneity in amplifying the propagation of shocks.

Another branch of the literature incorporates endogenous innovation, R\&D, and creative destruction into business-cycle models as both a source of firm heterogeneity and a 
new channel for technology shock propagation. Traditional RBC models take total factor productivity (TFP) as an exogenous process, but newer models allow TFP to evolve via 
the firm sector's innovation decision and diffusion of new technologies. This effectively brings Schumpeterian dynamics of innovation into the DSGE framework, enriching the 
set of propagation mechanisms.  A prominent example is the work by \textcite{comin2006medium}, and more recently \textcite{anzoategui2019endogenous}. Anzoategui et al. 
develop a medium-scale DSGE model where firms can spend on R\&D to improve the frontier technology and also incur costs to adopt existing innovations, and apply it to the 2008-09 recession. 
The authors find that the persistent productivity slowdown after the recession can, at large, be explained as an endogenous response to the drop in demand. In the model, the collapse in output 
and investment from the crisis led firms to cut R\&D and delay adoption of new technologies, causing TFP growth to falter.

On a similar note, other researchers have introduced idea production and knowledge spillovers into DSGE models. For instance,
some DSGE models feature an "innovation sector" producing new blueprints or product lines, similarly to \textcite{bilbiie2012endogenous},
but incumbent firms now decide whether to adopt new teechnologies, effectively separating variety creation from the firm dynamics.
\textcite{kung2015innovation} tie stock market valuations to R\&D-driven growth in a production economy, producing Schumpeterian dynamics: 
positive innovation shocks can cause burts of creative destruction that temporarily depresses output but raises growth later. That happens 
since a wave of new firm entry and old firm exit is unleashed by the innovation shock, leading to a reallocation of resources to a more 
optimal distribution. Conversely, and similarly to \textcite{sedlavcek2017growth}, adverse shocks can have prolonged recessionary effects
as the economy's idea pipeline dries up and less high-growth firms enter.


The frictions involved in creating new firms also play a fundamental role in dictating firm composition in an economy. There are many plausible 
sources of frictions worth considering. For instance, in the Sedláček-Sterk framework, a matching function dictates if entrants will find a matching
business idea, capturing how easily a would-be founder finds a business partner, investor or idea. \textcite{vardishvili2023entry} on the other hand,
study entrepreneurs' option to delay entry, causing a "wait-and-see" friction. The author argues that if entrepreneurs can pause plans until aggreagate
conditions improve, recessions will not only feature fewer entries, but also many delayed projects, leading to a surge of entry at the subsequent recovery.

Finally, there are welfare and policy implications to consider. In models like BGM, there is a variety externality issue, where individual firms do not internalize
that their entry adds consumer surplus by increasing variety. This might lead to under-entry in equilibrium, suggesting a possible socially inefficient equilibrium 
and arole for subsidies to startup formation. However, other potential distortions such as markups, fixed costs and financial frictioins might complicate the picture, 
not making it certain that more entry entry is always welfare-adding. Recent research by \textcite{bilbiie2019monopoly} tackles this issue by deriving optimal monetary
and fiscal policy in these settings, finding that the planner typically wants to encourage firm entry, especially during downturns, to offset the tendency of recessions
to reduce variety and future supply.

The integration of firm heterogeneity and endogenous entry into macroeconomics has opened up many questions. The fundamental debate with which I occupy myself
in this thesis is: How important is firm heterogeneity for macroeconomic fluctuations? Although \textcite{bilbiie2012endogenous} show that 
pro-cyclical startup entry amplifies business-cycle volatility, they treat all entrants as technologically identical, while \textcite{sedlavcek2017growth} 
highlight how recessions skew the composition of entrants through matching frictions but do so outside a love-of-variety RBC setting and with a different question of
firm employment in mind. By embedding Sedláček–Sterk’s technology-choice and matching block inside the BGM framework, 
this thesis delivers a DSGE model in which sector-specific returns-to-scale heterogeneity, entry-stage matching frictions, and endogenous idea supply shocks jointly shape 
and enrich the classic RBC shock propagation mechanisms. The model delivers a better picture of how aggreagte shocks can affect different types of firms in the economy, and
how this heterogeneity in turn affects aggregate outcomes through rich firm dynamics not explored in the standard BGM framework.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model}
\label{sec:model}

In this section, I briefly lay out the firm side in the baseline BGM model with no capital and CES preferences in subsection \ref{sec:model-bilbiie}, explain the Sedláček–Sterk
heterogeneity and matching friction mechanisms in subsection \ref{sec:model-sedlacek}, and finally, fully characterize the main model and the departures made
from the standard BGM framework in subsection \ref{sec:model-mine}. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Baseline Bilbiie-Ghironi Framework (CES Preferences)}
\label{sec:model-bilbiie}

In the original BGM framework, the key elements of the firm side are fully characterized by the production/labor decision 
and an entry decision pinned down by a free entry condition in equilibrium. I do not fully explore the consumer side of the framework yet for the sake of breviety, since it is analogous to the consumer side in the main model which will be 
explained in detail later. As described before in section \ref{sec:literature}, each firm (or production line) produces a unique variety $\omega$ using labor as their single 
production factor, with the production function 
\[
    y_t(\omega) = Z_t \cdot l_t(\omega),
\]
where $Z_t$ is the exogenous aggregate productivity level and $l_t(\omega)$ is the firm's labor input. Consumers have CES preferences over a continuum
of varieties 
\[
    C_t = \left[\int_{\omega \in \Omega_t} c_t(\omega)^{\frac{\theta-1}{\theta}}\,d\omega\right]^{\frac{\theta}{\theta-1}},
\]

which implies a consumption-based price index and constant markups for the firm. Solving the firm's pricing problem arrives in the equilibrium pricing
condition of

 \[
    \rho_t(\omega) = \frac{p_t(\omega)}{P_t} =  \mu \cdot \frac{w_t}{Z_t},
 \]

with $\mu=\frac{\theta}{\theta-1}$ and marginal costs corresponding to $\frac{w_t}{Z_t}$, which are simetrical across firms/varieties.

In the entry block, firms face a sunk entry cost $f_{E,t}$, expressed in effective labor units, and once firms have sucessfully entered, they survive
with probability $(1-\delta)$, where $\delta \in (0,1)$ is a "death shock". The law of motion dictating the total number of producers is 

    \[
    N_t = (1-\delta)(N_{t-1} + N_{e,t-1}),
    \]
where $N_{e,t}$ is the measure of new entrants, which face a time-to-build lag before entering. In equilibrium, the free-entry condition equates the expected present value of a firm's
future profit stream to the sunk cost in units of the consumption good, such that entry occurs until firm value is equalized with entry cost:

\[
    v_t(w) = \frac{w_t f_{E,t}}{Z_t}.
\]

Prospective entrants compute their expected post-entry value $v_t(\omega)$ given the present discounted value of their expected stream of profits
$\{d_s(\omega)\}_{s=t+1}^\infty$: 
$$v_{t}(\omega) = E_t \sum_{s = t+1}^{\infty} \left[ \beta (1 - \delta) \right]^{s - t} \left( \frac{C_{s}}{C_{t}} \right)^{-1} d_{s}(\omega).$$

In the BGM framework, this his also represents in the value of incumbent firms after production has happened, which is relevant for the household's investment decision.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Sedláček–Sterk Heterogeneity Mechanism}
\label{sec:model-sedlacek}

I abstract away from almost all other relevant model aspects presented by \textcite{sedlavcek2017growth} 
in this section to focus on two key mechanisms: the technology/returns-to-scale choice and the entry-stage 
matching friction. Before entry, each prospective entrepreneur/startup chooses a technology type $i\in\{1,\dots,I\}$,
which pins down the constant-returns-to-scale parameter $\alpha_i\in(0,1)$. Once active, an incumbent of age $a$ 
produces according to 
\[
y_{i,a,t}=A_t\,n_{i,a,t}^{\alpha_i},
\]
where $A_t$ is aggregate TFP and $n_{i,a,t}$ denotes employment. The heterogeneity in $\alpha_i$ implies 
heterogeneous optimal sizes for different startups, with size referring to the size of employment $n_{i,a,t}$ . Low-$\alpha_i$ firms remain small due to smaller scalability, whereas high-$\alpha_i$ firms can scale 
to thousands of workers over their life-cycle, matching empirical cohort size distributions. 

After a business-idea/technology-type is chosen, the firms faces the entry-stage matching friction. Let $e_{i,t}$ be
the measure of aspiring entrants that select technology $i$ at time $t$, and let $\psi_{i,t}$ denote the stock 
of business opportunities of type $i$ (with $\sum_i\psi_{i,t}=\Psi$). Because multiple entrants may chase the same idea, only
a fraction does actually succeed. Successful startups $m_{i,t}$ are generated by a Cobb-Douglas matching function

\[
m_{i,0,t}=e_{i,t}^{\phi}\psi_{i,t}^{\,1-\phi},
\]
where $\phi\in(0,1)$ is the matching elasticity, such that the success probability is pinned down by:

\[
P_{i,t}\;=\;\frac{m_{i,0,t}}{e_{i,t}}=e_{i,t}^{\,\phi-1}\psi_{i,t}^{\,1-\phi}.
\]

After paying the sunk entry cost $\chi$, a potential entrant earns expected value a potential entrant earns 
expected value $P_{i,t}V_{i,0,t}(0,F_t)$, where $V_{i,0,t}$ is the value of a newborn firm at time $t$ for technology type $i$.
Free entry therefore requires
\[
\chi \;=\;P_{i,t}V_{i,0,t}(0,F_t)\qquad\forall i,  \tag{FE}
\]
which pins down $P_{i,t}$ (and hence $m_{i,0,t}$) endogenously. In their quantitative implementation, the authors treat the 
probability $P_{i,t}$ as a fixed parameter due to data avaliability issues with $\psi_{i,t}$, which is a strategy also adopted
the main model presented later on.

The interaction between these two mechanisms creates rich firm dynamics. Because higher-$\alpha_i$ technologies yield 
larger $V_{i,0,t}$, condition (FE) forces their $P_{i,t}$ to fall—i.e.\ they face tougher matching—so shocks that 
shift the opportunity mix $\psi_{i,t}$ endogenously tilt the composition of entrants toward or away from high-growth firms. 
This joint mechanism of technology heterogeneity and matching frictions drives the persistent 
cohort‐quality effects documented before in section \ref{sec:literature}. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Model}
\label{sec:model-mine}

The model is a variant of the RBC model with endogenous firm entry and monopolistic competition found in \textcite{bilbiie2012endogenous}, from which
I make two departures based on the heterogeneity mechanism found in \textcite{sedlavcek2017growth}: i) multiple sectors with heterogeneity in
returns-to-scale parameters $\alpha_i$; ii) matching frictions for aspiring entrants choosing and attempting to enter a sector.

I accomodate the business-idea/technology choice mechanism by dividing the firm side of the economy into a finite number of sectors indexed by
$i \in \{1,2,...,I\}$. There is a continuum of unique firms/varieties indexed by $\omega \in \Omega$, with each one being fully defined by 
the unique product variety $\omega$ that it produces. I refer to firm $\omega$ that belongs to sector $i$ as "firm $\omega i$". 
I use $\Omega_i$ to denote the set that contains the indices of firms that belong to sector $i$, so that $\bigcup_{i=1}^{I} \Omega_i = \Omega$. 
Its measure, here denoted $M_{i}$, gives the size of the sector in term of firms (or production lines). I adopt the same interpretation as in BGM 
of understanding each firm/variety as production line rather than a separate entity, which also matches well with the scalability logic introduced
by a sectoral diversity in returns-to-scale parameters, as will be explored later in section \ref{sec:solution}.

\medskip
\medskip
\noindent\textbf{Households}
\medskip

The household framework is nearly identical to the one found in BGM, with the only difference being in their preference specification. There is a 
unit mass of atomistic, identical households. All contracts are nominal. Prices are flexible and thus I only solve for real variables. As the
composition of the consumption basket changes due to firm entry, I introduce money as an unit of account only, such that it plays no other role in the
economy and no modeling of money demand is necessary, resorting to a cashless economy as in BGM and \textcite{woodford2003interest}.

The Household supplies $L_t$ in a competitive labor market for $W_t$ and it maximizes $E_t \left[ \sum_{s=t}^{\infty} \beta^{s - t} U(C_s, L_s) \right]$ 
where $C$ is consumption and $\beta \in (0,1)$ the subjective discount factor. The period utility function follows the form 
$U(C_t, L_t) = \ln C_t - \chi \frac{(L_t)^{1 + 1/\varphi}}{1 + 1/\varphi}, \quad \chi > 0$ where $\varphi \geq 0$ is the Frisch elasticity
of labor supply to wages, and the intertemporal elasticity of substitution in labor supply. This choice of functional form makes sure that 
income and substitution effects of real wage variation on effort cancel out in steady state, as stated in BGM.

At time t, the household consumes the basket of goods $C_t$, defined over a continuum of goods $\Omega$. At any time, only $\Omega_t \in \Omega$ 
is available. Given sector $i$, the continuum of goods stemming from that sector are $\Omega_{i}$. Let $p_{i,t}(\omega)$ denote the nominal price 
of a good $\omega \in \Omega_{i,t}$. Additionally, demand for an individual variety, $c_{i,t}(\omega)$, is obtained as 
$c_{i,t}(\omega) \, d\omega = C_{i,t} \, \partial P_{i,t} / \partial p_{i,t}(\omega)$.

As in BGM but adapted to the sectoral framework here presented, the symmetric price elasticity of demand in sector $i$ $\zeta_i$  is a function 
of the number $M_{i,t}$ of goods/producers such that $\zeta (M_{i,t}) = (\partial c_{i,t}(\omega)/\partial p_{i,t}(\omega))(p_{i,t}(\omega)/c_{i,t}(\omega))$
, for any symmetric variety $\omega$. The benefit of additional product variety is here too described by the sectoral relative price $\rho_{i,t}(\omega) =
\rho(M_{i,t}) \equiv p_{i,t}/P_{i,t}$, for any symmetric variety $\omega$ in sector $i$, or in elasticity form $\epsilon(M_{i,t}) \equiv \rho'(M_{i,t})\,M_{i,t}/\rho(M_{i,t})$
. Together, $\zeta(M_{i,t})$ and $\rho (M_{i,t})$ completely 
characterize the effects of consumption preferences in this model. I define explicit functional forms for these objects later when specifying the 
functional form of preferences within and across sectors below.


\medskip
\medskip
\noindent\textbf{Firms}
\medskip

The firm block is defined as a collection of $I$ heterogeneous sectors with $M_{i,t}$ homogeneous firms each, 
facing two decisions: In which sector to enter and labor demand for each period after entering. There is continuum of monopolistically competitive
firms, each producing a different variety $\omega \in \Omega$, with one factor: Labor. 
Aggregate labor productivity is indexed by $Z_t$ (effectiveness of one unit of labor), which is 
exogenous, equal across sectors, and follows an $AR(1)$ process (in logarithms). For a firm that chooses sector $i$, the production function becomes
$y_{i,t}(\omega) = Z_t \cdot l_{i,t}(\omega)^{\alpha_i}$. Similar to the Sedláček–Sterk framework, firms chose a technology type/business-idea $i$ 
that determines their returns-to-scale parameter $\alpha_i$ and thus directly influences their marginal product of labor.

Prior to entry, the firm pays $f_{E,t}$ effective labor units, equal to $\frac{w_tf_{E,t}}{Z_t}$ units of the consumption good. 
Firms that enter the economy produce every period until they get hit with a "death shock" (probability $\delta \in (0,1)$ in every period). 
Entrants at time t can only start producing at time t+1, such that they incur a one period time-to-build lag. 
To produce a certain output level $y$, firms minimizes their labor cost in a static minimization problem
\[
    \min_{l_{i,t}(\omega)} \; w_t\,l_{i,t}(\omega) \quad \text{subject to} \quad y = Z_t \cdot l_{i,t}^{\alpha_i}(\omega),
\]
such that the optimal labor demand is then given at time $t$ in sector $i$ by 
\begin{equation}
  l_{i,t}^*(\omega) = \left(\frac{y}{Z_t}\right)^{\frac{1}{\alpha_i}},\label{eq:labourClearing}
\end{equation}
and therefore marginal costs are expressed as
\begin{equation}
  \text{MC}_{i,t} = \frac{w_t}{\alpha_i Z_t}\left(\frac{y_{i,t}(\omega)}{Z_t}\right)^{\!1/\alpha_i-1},\label{eq:marginalcost}
\end{equation}
which, differently from BGM, are sector specific and depend directly on the returns-to-scale parameter $\alpha_i$. However, the BGM
marginal cost expression is retrievable by setting $\alpha_i = 1, \, \forall i \in (i,1,...,I)$. With CES preferences, firms set relative
prices as constant markups over marginal costs 

\begin{equation}
  \rho_{i,t}(\omega) = \mu MC_{i,t}.\label{eq:pricing}
\end{equation}

As in BGM, but at the sectoral level, I assume a conditional symmetric firm equilibrium, where firms from the same sector 
are symmetric over prices, quantities and values. 
This implies that $p_{i,t}(\omega) = p_{i,t}, \ \rho_{i,t}(\omega) = \rho_{i,t}   , \   l_{i,t}(\omega) = l_{i,t}   , 
\  y_{i,t}(\omega) = y_{i,t}   , \  d_{i,t}(\omega) = d_{i,t}   ,  \ v_{i,t}(\omega) = v_{i,t}   , \  
\frac{p_{i,t}}{P_{i,t}} = \rho_{i,t} = \rho(M_{i,t})$. 

Therefore, profits/dividends for all firms in sector $i$ are identical and given by
\begin{equation}
  d_{i,t} = \Bigl(1-\tfrac1\mu\Bigr)\frac{C_{i,t}}{M_{i,t}}. \label{eq:profit}
\end{equation}

where $y_{i,t} = \frac{C_{i,t}}{M_{i,t}}$ since all firms are symmetrical and supply equal amounts of demand in their sector, analogous to firm-level
output in the BGM framework but adapted for the sectoral framework.

\medskip
\medskip
\noindent\textbf{Firm Entry with Uncertainty}
\medskip

The matching friction mechanism found in \textcite{sedlavcek2017growth} is adapted to the RBC framework presented here, such that firms face matching 
frictions in entering a sector and not all potential entrants are successful. In every time period $t$ and sector $i$, $\exists M_{i,t}$ mass of 
producing product lines an and unbounded mass of prospective entrants. The entrants are forward looking and correctly anticipate their future 
profits $d_{i,s}$ in every period $s\ge t+1$ as well as $\delta$ $\forall t$. Prospective entrants choose a technology type $i$ and corresponding sector.
Let technology types reflect returns-to-scale in increasing order such that $i = 1$ is lowest and $i = I$ is the highest. 
Let $e_{i,t}$ denote the measure of entrants choosing $i$ at time $t$. Not every attempt to enter is successful. The Cobb-Douglas  matching function 
is given by $m_{i,t}= e_{i,t}^{\phi}\,\psi_{i,t}^{\,1-\phi}$ such that $m_{i,t}$ are the successful entrants. $\psi_{i,t}$ is the measure of 
business opportunities for type $i$ at time $t$ and $\phi$ is a matching elasticity common across all types. 

In contrast with the Sedláček–Sterk formulation, in this new framework the overall measure of business ideas \(\Psi\) is not necessarily held constant,
being affected over time due to an exogenous aggregate stock of ideas shock \(X_t\), but its composition is. The motivation behind this change is that
the original formulation investigates how the composition of cohorts influences employment, whereas my model framework is interested in the aggregate 
effects of more business ideas being avaliable, not a shift in their distribution. To stay consistent with this new formulation, I specify the measure 
of business opportunities for technology \(i\) as 
\begin{equation}
  \psi_{i,t} =X_t^{\frac{1}{1-\phi}}\,\bar{\psi}_i, \label{eq:psilaw}
\end{equation}
where \(\bar{\psi}_i\) is the steady-state measure of business opportunities for technology \(i\), $X_t$ follows an AR(1) process of the type 
$X_t = 1 - \rho_X + \rho_X X_{t-1} + \epsilon^X_t$ where $\rho_X$ is a persistence parameter and $\epsilon^X_t$ are i.i.d innovations 
normally distributed with mean zero and variance $\sigma_X$. Consequently, the probability of a successful startup in sector $i$ is then:
\begin{equation}
  \Pi_{i,t} = \frac{m_{i,t}}{e_{i,t}} = e_{i,t}^{\phi-1}\,\psi_{i,t}^{\,1-\phi}. \label{eq:probability}
\end{equation}
Before entry, as in the BGM framework, prospective entrants compute their expected post-entry value by discounting the value of their expected stream
of profits $\{d_{i,s}\}_{s=t+1}^\infty$ as
\begin{equation}
  v_{i,t} = E_t \sum_{s = t+1}^{\infty} \left[ \beta (1 - \delta) \right]^{s - t} \left( \frac{C_{i,s}}{C_{i,t}} \right)^{-1} d_{i,s}, \label{eq:value}
\end{equation}
and thus entry occurs until firm value is equalized with entry cost, yielding the free entry condition for sector $i$ 
\begin{equation}
  \Pi_{i,t}v_{i,t} = f_{E,t}w_t/Z_t , \label{eq:freeentry}
\end{equation}
for all $i \in (1,2,..., I)$. This entry framework yields the new sectoral law of motion that dictates the number of incumbents in sector $i$, 
given by the following expression
\begin{equation}
  M_{i,t+1} = (1-\delta)(M_{i,t} + \Pi_{i,t}e_{i,t}). \label{eq:entrants}
\end{equation}
An important observation is that, as the demonstrated in BGM, there is no option value for waiting, since there remains no 
idiosyncratic/firm-specific uncertainty and exit constitutes an exogenous process, meaning that uncertainty related to firm death is also aggregate. 
Despite the introduction of matching frictions, every potential entrant faces the same matching probabilities $\Pi_{i,t}$ for each sector $i$ 
determined by aggregate conditions that are not firm-dependent\footnote{See the Appendix for the expanded BGM proof for my framework.}.

\medskip
\medskip
\noindent\textbf{Preference Specification and Markups}
\medskip

To capture heterogeneity across technology types, I adopt a two-layer aggregation process that nests the Dixit--Stiglitz framework at both 
the micro/sector and macro/aggregate levels, following \textcite{carvalho2021sectoral}. For each sector $i$, consumption is an aggreagte of the
continuum of varieties \(\omega \in \Omega_i\). Specifically, the type-\(i\) consumption bundle is defined as
\[
C_{i,t} \;=\; \left[ \int_{\omega \in \Omega_i} c_{i,t}(\omega)^{\frac{\theta-1}{\theta}}\,d\omega \right]^{\frac{\theta}{\theta-1}},
\]
and the corresponding price index is given by
\[
P_{i,t} \;=\; \left[ \int_{\omega \in \Omega_i} p_{i,t}(\omega)^{\,1-\theta}\,d\omega \right]^{\frac{1}{1-\theta}},
\]
where \(\theta \ge 1\) is the elasticity of substitution among varieties within sectors. By construction, total expenditure on goods in 
sector \(i\) is \(P_{i,t}C_{i,t}\). At the aggreagte level, the type-specific bundles \(\{C_{i,t}\}_{i=1}^I\) are 
aggregated into a final consumption basket. The final consumption aggregator is given by
\[
C_t \;=\; \left[ \sum_{i=1}^I \left( C_{i,t} \right)^{\frac{\eta-1}{\eta}} \right]^{\frac{\eta}{\eta-1}},
\]
with the overall price index defined as
\[
P_t \;=\; \left[ \sum_{i=1}^I \left( P_{i,t} \right)^{\,1-\eta} \right]^{\frac{1}{1-\eta}},
\]
where $\eta \ge 1$ is the elasticity across sectors. This top-level aggregation treats each technology type as a distinct variety, 
such that consumers can also substitute between sectoral bundles.

It follows that the household's demand for each good and sectoral good is 
$c_{i,t}(\omega) = \left(\frac{p_{i,t}}{P_{i,t}}\right)^{-\theta}C_{i,t}$ and 
$C_{i,t} = \left(\frac{P_{i,t}}{P_t}\right)^{-\eta}C_t$. Additionally, the markup and the within/across sector benefit of variety are 
independent of the number of goods, and related by $\epsilon = \mu -1 = 1/ (\theta-1)$. The CES expressions are then: 
$\mu(M_{i,t}) = \mu = \frac{\theta}{\theta - 1}, 
\   \epsilon_{\text{within}}(M_{i,t}) = \mu - 1 , \ \epsilon_{\text{across}}(N_{t}) = \eta - 1$ and most notably 
\begin{equation}
  \rho(M_{i,t}) = M_{i,t}^{\mu - 1} = \left(M_{i,t}\right)^{\frac{1}{\theta - 1}}. \label{eq:lovevariety}
\end{equation}

\medskip
\medskip
\noindent\textbf{Household Problem}
\medskip

As stated before in section \ref{sec:model-bilbiie}, the household problem here is analogous to the one found in BGM, since the consumers are
effectively "blind" to the sectoral diversity and consume a final aggregate basket of goods $C_t$. The only significant difference is regarding
the heterogeneity of the firms whose shares the household buys, but consumers only observe the aggregate quantities. Therefore, I define the aggregate
firm-level profit and value as 
$$
    d_{t} = \frac{\sum_iM_{i,t}d_{i,t}}{\sum_iM_{i,t}} \quad \text{and} \quad v_{t} = \frac{\sum_ie_{i,t}v_{i,t}}{\sum_ie_{i,t}},
$$
and $N_t$ as the measure of $\Omega_t$, representing the total number of incumbents in the economy at time $t$.

In this framework, there are 
2 types of assets that the household can buy in period $t$. The first are shares in a mutual fund for firms $x_t$ and the second are 
risk-free bonds $B_t$. Mutual funds pay a total profit in each period equal to the total profit of all firms that produce in $t$, namely $P_tN_td_t$. 
During $t$, the household buys $x_{t+1}$ shares in a mutual fund of $N_{H,t} = N_t + \mathcal{E}_{t}$ firms (those already operating at 
time $t$ and new potential entrants $\mathcal{E}_t = \sum_ie_{i,t}$), but only $N_{t+1} = (1-\delta)(N_t +N_{E,t})$ (where $N_{E,t} = 
\sum_im_{i,t}$) will produce and pay at time $t+1$, due to matching frictions and the death shock. The at $t$ price of a claim to the 
future profit stream of the fund of $N_{H,t}$ firms is equal to the nominal price of claims to future firm profits, $P_tv_t$.

Given this set-up, the period budget constraint for the representative household can be written as
$$B_{t+1} + v_t N_{H,t} x_{t+1} + C_t = (1 + r_t) B_t + (d_t + v_t) N_t x_t + w_t L_t,$$
where the left side represents expenditures including the purchase of new assets and consumption, and the left side represents income
including the dividends from firms, returns on bond stocks and labor income.

From this framework, I derive the first-order conditions of the household for optimal behaviour by solving the utility maximization problem,
yielding the Euler equation for bonds 
\begin{equation}
(C_t)^{-1} = \beta (1 + r_{t+1}) E_t \left[ (C_{t+1})^{-1} \right], \label{eq:eulerbonds}
\end{equation}
the Euler equation for share holdings in the fund of firms 
\begin{equation}
v_t = \beta (1 - \delta) E_t \left[ \left( \frac{C_{t+1}}{C_t} \right)^{-1} (v_{t+1} + d_{t+1}) \right], \label{eq:Eulershares}
\end{equation}
which, if iterated forward, yields the aggregate version of the relationship expressed by the firm valuation equation \eqref{eq:value}, and finally the intratemporal 
first-order condition 
\begin{equation}
\chi\,L_{t}^{1/\varphi}=\frac{w_t}{C_t}, \label{eq:intratemp}
\end{equation}
where $\varphi$ represents the frisch-elasticity of labor and $\chi$ is the
disutility of labor, as before\footnote{As in BGM, I omit the transversality conditions for bonds and shares that must be satisfied to
ensure optimality. Additionally, the interest rate is determined residually since it appears only in the Euler equation for bonds and is pinned
down once consumption is known.}.

\medskip
\medskip
\noindent\textbf{Aggregate Accounting, Equilibrium and the Labor Market}
\medskip

Under equilibrium, the following conditions hold for market clearing: $B_{t+1} = B_t=0$ and $x_{t+1}=x_t=1$ $\forall t$. Therefore, by applying these
equilibrium conditions to the household budget constraint and disaggregating firm-level variables, I arrive at the aggregate accounting identity
\begin{equation}
C_t + v_t\mathcal{E}_t= w_t.L_t + d_tN_t \;\Leftrightarrow\;C_t + \sum_iv_{i,t}e_{i,t}= w_t.L_t + \sum_id_{i,t}M_{i,t}, \label{eq:aggaccount}
\end{equation}
which states that the expenditure in consumption and investment in new firms must be equal to the income derived from labor and 
firm dividends in equilibrium.

Similar to the dynamic in the BGM baseline model, and in contrast to the standard one-sector RBC model of \textcite{campbell1994inspecting}, 
the model presented here has two "macro-sectors", such that one employs part of the labor supply to produce consumption goods and the other
sector employs the rest of the labor supply to establish new production-lines/firms. Consequently, the economy's GDP $Y_t$ is simultaneously
equal to total income $w_t.L_t + \sum_id_{i,t}M_{i,t}$ and the total output of the economy $C_t + \sum_iv_{i,t}e_{i,t}$, and $v_{i,t}$ represents 
the relative price of investment in terms of consumption.

As a direct consequence of the two-sector nature of my model, the labor market equilibrium is characterized by $L^C_t+L^E_t = L_t$, that is, 
the total labor is equal to the labor used in production $L^C_t = \sum_iM_{i,t}\ell_{i,t}$ at time $t$ plus the total labor 
used to build firms $L^E_t = \sum_ie_{i,t} f_{E,t}/Z_t$ at time $t$. Entry determines the amount of labor allocated to setting 
up new production lines, such that entry at time $t$ affects labor demand in time $t+1$. Therefore, aggregate labor clearing can be expressed as
\begin{equation}
 L_t = \underbrace{\sum_i M_{i,t}l_{i,t}}_{\text{production}} + \underbrace{\sum_i e_{i,t}f_{E,t}/Z_t}_{\text{entry}}.\label{eq:AgglabourClearing}
\end{equation}
Matching frictions, however, introduce a dynamic where not all the labor spent in building new firms is actually fruitful. 
Labor is used at producing firms that might not actually survive the matching
process, especially for highly scalable sectors that have lower probabilities of successful entry.

\medskip
\medskip
\noindent\textbf{Characterizing Equilibrium}
\medskip

Given predetermined variables $M_{i,t}$, $\psi_{i,t}$, $r_t$ and exogenous shocks $(Z_{t},X_{t}, f_{E,t})$\footnote{Note: I treat 
$f_{E,t}$ as a parameter during quantitative exercises}, the intra-period sequence in the model goes as follows: i) Given their preferences, households
choose $\{C_t,L_t,B_{t+1},x_{t+1}\}$; ii) Incumbent firms hire labor, set prices, produce and pay dividends in all sectors;
iii) Potential entrants pay the sunk entry cost $f_{E,t}w_t/Z_t$.  Matching occurs with probability $\Pi_{i,t}$ and 
successful entrants $m_{i,t}$ join $M_{i,t+1}$ in all sectors $i$ (time-to-build); iv) Exogenous shocks $(Z_{t+1},X_{t+1})$ realise and 
date $t{+}1$ begins.

Out of the 15 main equations highlighted above, many of the variables introduced are merely definitions and/or identities that add no new 
information to the system. 
For instance, the definition of firm level output and labor demand \eqref{eq:labourClearing} simply build $y_{i,t}$ and $l_{i,t}$ 
once \( C_{i,t} \), \( M_{i,t} \) are known. Additionally, the aggregate consumption index $C_t$ is not included since it is mechanically 
defined once $C_{i,t}$ is known for each sector, adding no information to the system. Therefore, I do not include 
the aggregate goods clearing condition as an equilibrium condition, since it does not pin down any additional variable.
Furthermore, nominal variables like $P_{i,t}$ and $p_{i,t}$ are not solved for, since, with CES preferences, blocks 
\eqref{eq:pricing} and \eqref{eq:lovevariety} solve for the real/relative sectoral price $\rho_{i,t}$


Therefore, equilibrium can be characterized as follows: Given exogenous processes $(Z_t,X_t,f_{E,t})$, initial masses $\{M_{i,0}\}$, 
and a top-level price numéraire $P_t \equiv 1$ as a nominal anchor, I summarize equilibrium as a sequence 
\[
\bigl\{\,w_t^*,L_t^*,r_{t}^*,\bigl\{
        M_{i,t}^*,C_{i,t}^*,\rho_{i,t}^*,d_{i,t}^*,v_{i,t}^*,e_{i,t}^*,\psi_{i,t}^*,\Pi_{i,t}^*\bigr\}^I_{(i=1,\dots,I)}\bigr\}.
\]
of 3 + 8$I$ endogenous variables, with 3 variables being predetermined at time $t$ ($M_{i,t}$, $r_t$ and $\psi_{i,t}$), 
satisfying the simplified system of equilibrium conditions in Table \ref{tb:eqconditions} out of all the relevant equations explored in section \ref{sec:model-mine}

\begin{table}[H]
\centering
\renewcommand{\arraystretch}{1.4}
\begin{tabularx}{\textwidth}{@{}>{\raggedright\arraybackslash}p{0.4cm} >{\raggedright\arraybackslash}p{3.5cm} X c@{}}
\toprule
\textbf{} & \textbf{Type} & \textbf{Equation(s) in Section 3} & \textbf{Dimension} \\
\midrule
1 & Pricing Rule in sector $i$ & \(  \rho_{i,t} = \mu \, \frac{w_t}{\alpha_i Z_t}\left(\frac{y_{i,t}}{Z_t}\right)^{\!1/\alpha_i-1}  \quad \text{combining \eqref{eq:pricing} and \eqref{eq:marginalcost}} \) & \( I \) \\
2 & Variety Effect in sector $i$ & \(  \rho_{i,t} = M_{i,t}^{\frac{1}{\theta-1}}  \quad \text{ from \eqref{eq:lovevariety}} \) & \( I \) \\
3 & Profits in sector $i$ & \(d_{i,t} = \Bigl(1-\tfrac1\mu\Bigr)\frac{C_{i,t}}{M_{i,t}} \quad \text{ from \eqref{eq:profit}}\) & \( I \) \\
4 & Firm valuation in sector $i$ & \(v_{i,t}=\beta(1-\delta)E_t\Bigl[\bigl(C_{i,t+1}/C_{i,t}\bigr)^{-1}\bigl(v_{i,t+1}+d_{i,t+1}\bigr)\Bigr]\quad \text{from \eqref{eq:value}}\) & \( I \) \\
5 & Free entry in sector $i$ & \(  \Pi_{i,t}=\frac{f_{E,t}\,w_t}{Z_tv_{i,t}}  \quad \text{ from \eqref{eq:freeentry}} \) & \( I \) \\
6 & Stock of ideas in sector $i$ & \(  \psi_{i,t}=X_t^{\frac{1}{1-\phi}}\psi_i^{ss}  \quad \text{ from \eqref{eq:psilaw}} \) & \( I \) \\
7 & Matching definition & \( e_{i,t} = \psi_{i,t}\bigl(\Pi_{i,t}\bigr)^{\frac{1}{\phi-1}} \quad \text{from \eqref{eq:probability}} \) & \( I \) \\
8 & Number of firms in sector $i$ & \( M_{i,t+1} = (1-\delta)\bigl(M_{i,t}+e_{i,t}\Pi_{i,t}\bigr) \quad \text{from \eqref{eq:entrants}} \) & \( I \) \\
9 & Intra-temporal labour FOC & \( \chi L_t^{1/\phi} = \frac{w_t}{C_t} \quad \text{from \eqref{eq:intratemp}} \) & \( 1 \) \\
10 & Inter-temporal Euler (bonds) & \(1 = \beta(1+r_{t+1})E_t\Bigl[\tfrac{C_t}{C_{t+1}}\Bigr] \quad \text{from \eqref{eq:eulerbonds}} \) & \( 1 \) \\
11 & Aggregate Labor Identity & \( L_t=\sum_i(M_{i,t}\ell_{i,t}+e_{i,t} f_{E,t}/Z_t) \ \  \ \text{from \eqref{eq:AgglabourClearing}}\) & \( 1 \) \\
\midrule
\multicolumn{3}{r}{\textbf{Total independent conditions}} & \( 3 + 8I \) \\
\bottomrule
\end{tabularx}
\caption{Equilibrium Equations and Dimensionality}
\label{tb:eqconditions}
\end{table}

The household Euler equation for shares is left out of the list of equilibrium conditions as in BGM because it represents the same relationship 
as the firm valuation equation but at an "average" aggregate level. Since I am interested in the sectoral profit and firm value dynamics, I omit it from the 
equilibrium conditions. Finally, when building the "$3 + 8I$" system, I keep only three unknowns per sector for the 
matching-entry block, $ e_{i,t},  \psi_{i,t}$ and $\Pi_{i,t}$. The auxiliary object \( m_{i,t} \) is left out of the list, 
precisely because it is mechanically pinned-down once \( (M_{i,t}, e_{i,t}, \psi_{i,t},\Pi_{i,t}) \) are known.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model Solution and Properties}
\label{sec:solution}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sector–by–Sector Steady State}
\label{sec:solution-steadystate}

To derive the steady-state expressions for all variables, I divide the solution into $I$ sectoral blocks and one aggregate block, to stay consistent
with the formulation of equilibrium in section \ref{sec:model-mine}. I normalize aggregate productivity $Z = 1$ and set the stock of ideas shock
$X = 1$ in steady state, but I keep the variables in the expressions for tractability. Every variable is constant over time and thus time subscripts
are dropped. Otherwise, the notation matches the main model description in section \ref{sec:model-mine}.

From the intertemporal Euler equation for bonds, the steady-state interest rate is already pinned down by $1+r = \beta^{-1}$. I follow 
BGM and \textcite{campbell1994inspecting} and make use of $1+r = \beta^{-1}$ to treat $r$ as a parameter in the solution. The firm valuation
equation \eqref{eq:value} together with the definition $\kappa=\frac{r+\delta}{1-\delta}$ yields $v_i = d_i/\kappa$, which captures a premium for
the expected firm destruction, since a higher $\delta$ brings down the price of the investment "good" (\textit{ceteris paribus}). Combining 
this expression with the free-entry condition \eqref{eq:freeentry}and substituting in the definition of profits \eqref{eq:profit} I arrive at  
\begin{equation}
  \frac{C_i}{M_i}=\frac{\kappa\,w f_E}{Z\Pi_i(1-1/\mu)}, \label{eq:CoverM}
\end{equation}
which pins down the ratio between sectoral consumption and the number of firms as a function of model parameters and the probability of successful 
entry in sector $i$, which is also the definition of firm-level output $y_i$. This expression helps pin down in steady state all 
variables dependent on $y_i$ such as $\ell_i$ with equation \eqref{eq:labourClearing}, $MC_i$ with equation \eqref{eq:marginalcost} and 
$\rho_i$ with \eqref{eq:pricing}. 

Expression \eqref{eq:CoverM} hints at the fundamental role that competition plays in pinning down firm-level
behaviour in the conditional symmetric firm equilibrium. Almost counterintuitively, an increase in the death-rate, real wage or sunk entry-cost all lead
to an increase in the firm-level output and labor demand, given that all these changes decrease the incentives for entering sector $i$. This, in turn,
means that active incumbents in sector $i$ have less competing firms with whom to share the market with, leading to a higher level of output and larger
firm size despite the negative impact of an increase in wages and the death rate. 

The heterogeneous behavior of potential entrants and active incumbents comes from the fact that, after the forward-looking choice of entry, 
successful entrants only perform the myopic-static choice of optimal labor demand every period, and do not take into consideration their probability
of death, since exit is an exogenous process. Additionally, the negative impact of a wage surge on the labor decision is counterbalanced by the 
positive impact of a decrease in incumbents due to rising entry costs on within-sector competition, hence the positive impact of wage on firm-level output 
and employment.

Finally, an increase in the probability of successful matching also drives up entry, since an increase in $\Pi_i$ raises the expected payoff of attempting
an entry in sector $i$. In steady state, wage rises one-to-one with productivity since the marginal product of labor (MPL) is 
$MPL_i = \alpha_i Z l_i^{\alpha_i -1}$, such that only the ratio $w/Z$ actually matters, and thus a momentary increase in $Z$ has no direct impact
on firm-level output in a steady-state static equilibrium. Markups also have an interesting impact on firm-level output and size, where an increase in markups drives down firm level output
despite driving firm-level profits up, since again, entry appears more attractive to prospective entrepreneurs, leading to more competition and lower
output.

% By equating the relative-price expression \eqref{eq:pricing} combined with the definition of marginal costs 
% \eqref{eq:marginalcost} with the love-for-variety expression \eqref{eq:lovevariety}, and inserting expression \eqref{eq:CoverM}, the result is
% one scalar equation pinning down $M_i$ in steady state as a function of model parameters and $\Pi_i$:
% \begin{equation}
%   M_i^{\frac1{\theta-1}} =\mu\,\frac{w}{Z\alpha_i}\Bigl[\frac{\kappa\,w\,f_E}{Z(1-1/\mu)\,\Pi_i}\Bigr]^{\frac1{\alpha_i}-1}. \label{eq:Misolated}
% \end{equation}
% This expression allows the determinants in steady state of the number of firms/production lines to be more clearly visualized. Higher markups, as
% discussed for expression \eqref{eq:CoverM}, lead to higher prospective profits and a higher number prospective and successful entrants. However, 
% the same higher markup also hinders household demand for goods, which pushes down profits and thus the expected value of entry. When technology is 
% sufficiently scalable (high $\alpha_i$), the per-unit-profit gain outweighs the quantity loss, so the positive channel dominates and $M_i$ rises. 

% An increase in the $w/Z$ ratio for, say, an increase in the real wage, leads to a smaller number of active incumbents due to higher entry costs 
% and operating costs, hindering entry attempts.\textbf{FINISH LATER}

As for the sectoral entry-matching block, combining the law-of-motion of incumbents \eqref{eq:entrants} and the matching 
definition \eqref{eq:probability} both in steady state yields 
\begin{equation}
m_i= e_i\Pi_i= \frac{\delta}{1-\delta}M_i. \label{steadyentrants} 
\end{equation}
That is, the number of successful new entrants $m_i$ makes up for the exogenous destruction of new firms, and the 
number of prospective new entrants $e_i$ also compensates for the probability $\Pi_i$ in each sector of successful
matching actually taking place.

The aggregate accounting identity \eqref{eq:aggaccount} in steady state is also particularly informative when it
comes to understanding the general structure of the model. By substituting in the free entry condition 
\eqref{eq:freeentry}, matching probability definition \eqref{eq:probability} and the law of motion of incumbents \eqref{eq:entrants} all
in steady state, the identity now becomes:
\begin{equation}
C + \frac{w f_E}{Z}\frac{\delta}{1-\delta}\sum_iM_{i}= w.L + \frac{w f_E}{Z}\kappa \sum_i\frac{M_i}{\Pi_i}. \label{aggsteadystate} 
\end{equation}
The same general idea of matching expenditure (consumption plus investment) with income (labor income plus dividends)
in a two "macro-sector" economy remains. However, investment and dividends can be broken down into further detail. 

Investment, on one hand, now captures the replacement principle seen in the classical RBC model 
(See \cite{campbell1994inspecting}) more clearly, where investment is made at steady state as pure maintenance to keep the variety/firm stock from shrinking. Therefore,
a higher death rate immediately requires more labor being spent on producing new firms. Dividends, on the other hand, represent in
steady state the profits required to finance this replacement. A higher death rate, through $\kappa$, makes households require 
higher payoffs to keep financing new entry. Better matching in the form a higher $\Pi_i$ also frees up profits that can go to 
consumption or lower labor effort, an effect that is masked in the non-static version \eqref{eq:aggaccount} because $e_{i,t}$ 
simultaneously adjusts on the investment side.

The steady state specification for all other variables in the system can be found in the appendix \textbf{WHERE???}. The blocks are,
as discussed previously, divided into sectoral and aggregate. Due to concerns introduced by the heterogeneous sectoral blocks, no
one-size-fits-all closed form steady state solution can be found, mainly due to the real wage. For that matter, I solve for the
steady state values of all variables using an outer-inner loop dynamic explored in the following section \ref{sec:solution-num}.
Subsequently, I explore these results in section \ref{sec:solution-properties}, with a particular focus on firm dynamics, the
composition of the firm sector, and the implications of introducing heterogeneity through the returns-to-scale parameter $\alpha_i$.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Numerically Solving the Steady State}
\label{sec:solution-num}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Properties of the Steady-State}
\label{sec:solution-properties}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quantitative Implementation}
\label{sec:quant}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Calibration}
\label{sec:quant-cal} 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Impulse responses}
\label{sec:quant-IRF}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Concluding Remarks}
\label{sec:conclusion}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% References section
\newpage
\thispagestyle{plain}
\pagenumbering{Roman}
\printbibliography[heading=bibintoc] % Insert references

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendices section
\newpage
\begin{refsection}
\thispagestyle{plain}
\pagenumbering{arabic}  % Turn page numbering to arabic
\renewcommand*{\thepage}{A-\arabic{page}} % Add 'A' to each page number for appendices section
\addtocontents{toc}{\protect\setcounter{tocdepth}{1}} % This hides the appendix subsections in the table of contents
\begin{appendices}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Additional Figures}
\label{sec-app:full}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Computational Implementation}
\label{sec-app:codes}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data for Model Calibration}
\label{sec-app:data}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Supplementary Results}
\label{sec-app:figures}

This appendix contains supplementary figures and tables, placed here for the sake of brevity in the main text. It is ordered according to the corresponding sections in the text.



\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{appendices}
\thispagestyle{plain}
\pagenumbering{Roman} % Start Roman page numbering for appendix references
\renewcommand*{\thepage}{A-\Roman{page}} % Add 'A' to each page number for appendix references

\addcontentsline{toc}{section}{Appendix References}
\printbibliography[heading=subbibliography, title={Appendix References}]
\thispagestyle{plain}
\cleardoublepage % Ensure the next content starts on an odd page (if your document is two-sided)

\end{refsection}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\thispagestyle{plain}
\pagenumbering{gobble} % Turn page numbering off
\section*{Statement of Authorship} % Include statement of authorship
I hereby confirm that the work presented has been performed and interpreted solely by myself except for where I explicitly identified the contrary. I assure that this work has not been presented in any other form for the fulfillment of any other degree or qualification. Ideas taken from other works in letter and in spirit are identified in every single case.

\vspace{2cm}
\noindent
\rule{8cm}{0.4pt}\\
Enrico Truzzi\\
Bonn, the \printdate{2025-7-1}
\end{document}
% End Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
